Corpus Stats

### 2019-03-26 notebooks/corpus_stats_and_plots.Rmd
notebooks

records_by_fun$pkg <- factor(records_by_fun$pkg, levels=combo_df$package_name)
# log scale?
# records_by_fun$invo_obs <- sapply(records_by_fun$invo_obs, function(x) if (x == 0) x else log10(x))

plot_records <- ggplot(data=records_by_fun, aes(x=invo_obs, y=invo_rec)) +
                geom_point(size=0.25) + 
                labs( title = "Numbers of Observed Signatures",
                      y = "Recorded Invocations in Pkg (Thousands)",
                      x = "Observed Invocations in Pkg (Thousands)") +
                theme(axis.text.x = element_blank(), axis.title.x=element_blank(),
                      axis.ticks.x=element_blank()) #+
                # scale_y_continuous(breaks = c(0, 1, 2, 3, 4, 5, 6),
                #      labels = c(0, 10, 100, 1000, 10000, 100000, 1000000))

>>>>

records_by_fun$pkg <- factor(records_by_fun$pkg, levels=combo_df$package_name)
# log scale?
# records_by_fun$invo_obs <- sapply(records_by_fun$invo_obs, function(x) if (x == 0) x else log10(x))
# records_by_fun$invo_rec <- sapply(records_by_fun$invo_rec, function(x) if (x == 0) x else log10(x))

plot_records <- ggplot(data=records_by_fun, aes(x=invo_rec, y=invo_obs)) +
                geom_point(size=0.25) + 
                labs( title = "Numbers of Observed Signatures",
                      y = "Obs Invocations in Pkg",
                      x = "Rec Invocations in Pkg")
                # theme(axis.text.x = element_blank(), axis.title.x=element_blank(),
                #       axis.ticks.x=element_blank()) #+
                # scale_y_continuous(breaks = c(0, 1, 2, 3, 4, 5, 6),
                #      labels = c(0, 10, 100, 1000, 10000, 100000, 1000000))
